Outline

### 2020-06-05 Outline.Rmd
Add working title to outline
Starting to work on possible outline

---
title: "Outline"
output: html_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
---

@@

Journal: Current Landscape Ecology Reports
Type: Methodological Developments in Landscape Ecology

@@

< **TITLE** >

@@

Keywords: keyword 1, keyword 2, keyword 3, keyword 4, keyword 5, …

### 1. Introduction
- First topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- Second topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- ...
- Last topic (often objectives and hypotheses)
    - ...

### 2. Methods
- First topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- Second topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- ...
- Last topic
    - ...

### 3. Results (same structure and order as Methods)
- First topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- Second topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- ...
- Last topic (often objectives and hypotheses)
    - ...

### 4. Discussion
-	Possible points to discuss
    - First point
    - Second point
- ...
- Conclusions
    - Conclusion 1 
    - Conclusion 2
    - ...

@@

### Open questions:
- ...
- ...

>>>>

---
title: "Outline"
output: html_document
theme: cosmo
date: '`r format(Sys.time(), "%d %B, %Y")`'
editor_options: 
  chunk_output_type: console
---

@@

Journal: Current Landscape Ecology Reports

Type: Methodological Developments in Landscape Ecology

@@

Title: **Open source landscape ecology tools**

@@

Keywords: keyword 1, keyword 2, keyword 3, keyword 4, ...

### 1. Introduction
- Intro to landscape ecology
    - How do landscape characteristics influence ecological processes and vice verse
    - Growing importance because often scales of policy making are adressed
    - Need to preprocess, modify, model and analyze spatial data
    - Short overview over common tasks/analysis in landscape ecology
    - ...
- Intro to open-source
    - What is open-source and why is it advantageous to closed source
    - R environment
    - ...
- Landscape ecology in R
    - One of the most used tools/powerful tool in ecology and spatial data analysis
    - History of landscape ecology/spatial data analysis in R
    - Growing body of specific textbooks and literature; e.g.:
        - "Geocomputation with R"
        - "Spatial Data Science"
        - "Spatial Ecology and Conservation Modeling. Applications with R"
        - "Learning Landscape Ecology. A Practical Guide to Concepts and Techniques"
        - ...
    - Growing body of specific R package for spatial data analysis
    - ...
- Objectives of review
    - Existing/important R packages for landscape ecology
    - Missing packages R packages for landscape ecology
    - ...
- ...

### 2. Existing packages
- Basic spatial data
    - Basic data types (i.e. vector vs. raster data)
        - raster, stars, terra(?)
        - sp, sf
        - rgeos, rgdal
        - ...
    - Creating maps
        - maptools, tmap, ggplot2
        - ...
- Web-mapping frameworks
    - mapview, leaflet
    - ...
- Spatial regression
    - nlme, spdep, kriging
    - ...
- Ecological analysis
    - Landscape metrics
        - landscapmetrics
        - ...
    - Habitat selection and SDM
        - ade4, sdm
        - ...
    - Various
        - vegan
        - NLMR
    - ...
- ...
### 3. Missing packages
- First topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- Second topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- ...
- Last topic (often objectives and hypotheses)
    - ...

### 4. Discussion
- Possible points to discuss
    - First point
    - Second point
    - ...
- ...
- Conclusions
    - Conclusion 1 
    - Conclusion 2
    - ...
- ...

@@

### Open questions:
- Remote sensing/GIS?
- Landscape genetics?
- Landscape Connectivity?
- Some "results"/meta-analysis of increase of R in landscape ecology?
- Missing packages
    - surface metrics
    - vector-based metrics
- ...
